PAMELA: an annotation-based Java Modeling Framework

### 2021-02-04 architecture.tex
remove reference to PAMELA semantics
add a reference to other feature

\begin{itemize}
    \item \texttt{@ModelEntity}: tag annotating \texttt{interface} as \emph{ModelEntity}. May declare an abstract entity.
    \item \texttt{@ImplementationClass}: tag annotating \emph{ModelEntity} \texttt{interface} and precising abstract Java \texttt{class} to be used as base implementation.
    \item \texttt{@Implementation}: tag annotating a partial implementation (abstract inner \texttt{class} defined in implemented \texttt{interface}), and used in the context of multiple inheritance.
    \item \texttt{@Getter(String)}: tag annotating method as unique getter for implicit \emph{ModelProperty} whose identifier is the declared String value. May also declares cardinality, eventual inverse property, default value and some other features.
    \item \texttt{@Setter(String)}: tag annotating method as unique setter for implicit \emph{ModelProperty} whose identifier is the declared String value.
    \item \texttt{@Adder(String)}: tag annotating method as unique adder for implicit multiple cardinality \emph{ModelProperty} whose identifier is the declared String value.
    \item \texttt{@Remover(String)}: tag annotating method as unique remover for implicit multiple cardinality \emph{ModelProperty} whose identifier is the declared String value.
    \item \texttt{@Reindexer(String)}: tag annotating method as unique reindexer for implicit multiple cardinality \emph{ModelProperty} whose identifier is the declared String value.
    \item \texttt{@Initializer}: tag annotating a method used as a constructor for related \emph{ModelEntity}.
   \item \texttt{@Deleter}: tag annotating a method used as explicit destructor for related \emph{ModelEntity}.
    \item \texttt{@Finder(String,String)}: tag annotating method as a fetching request for a given \emph{ModelProperty} with a given attribute.
    \item \texttt{@CloningStrategy}: allows to customize cloning strategy for a given \emph{ModelProperty}.
    \item \texttt{@Embedded}: allows to declare a given \emph{ModelProperty} as embedded according to PAMELA semantics.
    \item \texttt{@Imports} and \texttt{@Imports}: allows to declare some entities to be included in PAMELA model.
    \item \texttt{@XMLElement} and \texttt{@XMLAttribute}: used to specify XML serialization for PAMELA instances.

@@

\ab{Programmers may already reuse} a number of advanced programming features (some already mentioned) such as:  multiple inheritance and traits, containment management, cloning, fine-grained notifications management, object graph comparison and diff/merge, visiting patterns, clipboard management, validation, support for \emph{design by contract} by integrating assertions from Java Modeling Language (JML), Metaprogramming, Aspect Oriented Programming. \ab{Experimented programmers may extend PAMELA defining new annotations.}

>>>>

\begin{itemize}
    \item \texttt{@ModelEntity}: tag annotating \texttt{interface} as \emph{ModelEntity}. May declare an abstract entity.
    \item \texttt{@ImplementationClass}: tag annotating \emph{ModelEntity} \texttt{interface} and precising abstract Java \texttt{class} to be used as base implementation.
    \item \texttt{@Implementation}: tag annotating a partial implementation (abstract inner \texttt{class} defined in implemented \texttt{interface}), and used in the context of multiple inheritance.
    \item \texttt{@Getter(String)}: tag annotating method as unique getter for implicit \emph{ModelProperty} whose identifier is the declared String value. May also declares cardinality, eventual inverse property, default value and some other features.
    \item \texttt{@Setter(String)}: tag annotating method as unique setter for implicit \emph{ModelProperty} whose identifier is the declared String value.
    \item \texttt{@Adder(String)}: tag annotating method as unique adder for implicit multiple cardinality \emph{ModelProperty} whose identifier is the declared String value.
    \item \texttt{@Remover(String)}: tag annotating method as unique remover for implicit multiple cardinality \emph{ModelProperty} whose identifier is the declared String value.
    \item \texttt{@Reindexer(String)}: tag annotating method as unique reindexer for implicit multiple cardinality \emph{ModelProperty} whose identifier is the declared String value.
    \item \texttt{@Initializer}: tag annotating a method used as a constructor for related \emph{ModelEntity}.
   \item \texttt{@Deleter}: tag annotating a method used as explicit destructor for related \emph{ModelEntity}.
    \item \texttt{@Finder(String,String)}: tag annotating method as a fetching request for a given \emph{ModelProperty} with a given attribute.
    \item \texttt{@CloningStrategy}: allows to customize cloning strategy for a given \emph{ModelProperty}.
    \item \texttt{@Embedded}: allows to declare a given \emph{ModelProperty} as
      embedded. %according to PAMELA semantics.
    \item \texttt{@Imports} and \texttt{@Imports}: allows to declare some entities to be included in PAMELA model.
    \item \texttt{@XMLElement} and \texttt{@XMLAttribute}: used to specify XML serialization for PAMELA instances.

@@

\ab{Programmers may already reuse} a number of advanced programming features
(some already mentioned) such as: multiple inheritance and traits, containment
management, cloning, fine-grained notifications management, object graph
comparison and diff/merge, visiting patterns, clipboard management, validation,
support for \emph{design by contract} by integrating assertions from Java
Modeling Language (JML), Metaprogramming, Aspect Oriented Programming. Each of
those features is described on a dedicated page that is reachable from the
official web site\footnote{\url{https://pamela.openflexo.org/SNAPSHOT/}}.
\ab{Experimented programmers may extend PAMELA defining new annotations.}
